\input{shared/ietf-slides.tex}

\title{URI-Path abbreviation in CoAP}
\subtitle{\ietfdraft{ietf-core-uri-path-abbrev-04}}
\author{\textit{Christian~Amsüss}, Michael~Richardson}
\date{2026-03-20, CoRE at IETF125}

\begin{document}

\frame{\titlepage}

\begin{frame}{\color{gray}Why?}\Large\color{gray}
  GET /.well-known/core has 17 bytes of Uri-Path.

  \bigskip

  EDHOC was unhappy.

  \bigskip

  cBRSKI is unhappy.

  \bigskip

  IETFers are jealous of other SDOs\footnote{LwM2M's \texttt{/rd} is a BCP190 no-go}
\end{frame}

\begin{frame}{\color{gray}Solution}\Large\color{gray}
  Numeric Uri-Path-Abbrev option.

  \bigskip

  \begin{tabular}{l|l}
    Abbreviated & Expanded \\ \hline
    Uri-Path: 0 \hspace{1cm} & Uri-Path: ``.well-known'', ``core'' \\
    \texttt{d0 00} & \texttt{bb . w e l l - k n o w n 04 c o r e} \\
    2 & 17 \\
  \end{tabular}

  \bigskip

  Critical. Safe-to-forward\footnote{even though Uri-Path is not}.

  \bigskip

  Uri-Host (3), Uri-Port (7), \textbf{Uri-Path-Abbrev (13)}, Uri-Query (15).
\end{frame}

\begin{frame}{Open items after IETF124}\Large
  \framesubtitle{Part I: Move in \ietfdraft{ietf-core-corr-clar} Section 2.2 (\href{https://github.com/core-wg/uri-path-abbrev/pull/32}{PR \#32})}

  Now appendix A, updating RFC7252:
  
  \bigskip

  ``Unrecognized critical options cause 4.02 Bad Option \textit{even for NON}''.
  
  \vspace{1cm}

  \begin{itemize}
    \item Only affects tentative use.
    \item Still expect RST/silence: deployed behavior.
    \item Practical simplification: when only UPA support is known and just value is tentative.
  \end{itemize}
\end{frame}

\begin{frame}{Open items after IETF124}\Large
  \framesubtitle{Part II: Simplify Proxy-Uri intraction}

  PRs \href{https://github.com/core-wg/uri-path-abbrev/issues/33}{\#33} and \href{https://github.com/core-wg/uri-path-abbrev/issues/38}{\textit{\#38}}\footnote{\label{yester}My apologies for the short-notice changes -- but presenting them in a single change is still better than giving you half of it here and half of it in the next interim.}
  
  \begin{itemize}
    \item Mixed Uri-Path + Uri-Path-Abbrev: consistently disallowed.

      % now consistently "just unusable when meddling with paths": that does simply break general applications (not just this one).

      If proxies would introduce path segments,
      service can't support UPA.
      % no use cases, needless complication.
    \item \textit{As the last hop is not to a forward-proxy, servers will never see Proxy-Uri effects.\footnote{Ongoing corr-clar issue \href{https://github.com/core-wg/corrclar/issues/51}{\#51}.}}
      \bigskip

      \textit{$\Rightarrow$ replaced general ``SHOULD understand'' for mixed case with ``MUST'' for server-proxy hybrids.}
  \end{itemize}
\end{frame}

\begin{frame}{Open items after IETF124}\Large
  \framesubtitle{Part III: Addressing reviews}
  \begin{itemize}
    \item Clarify that Uri-Path and UPA conflict means UPA is the Bad Option.
    \item Editorial changes after reviews from Carsten and Esko.
  \end{itemize}
\end{frame}

\begin{frame}{Next steps}\Huge
  Done.
\end{frame}

\begin{frame}{\color{gray}Backup: Applications}\large
  \begin{description}[\texttt{-responses}]
    \item[\color{gray}EDHOC] \color{gray}first 3 message total: -30 byte down to 122\footnote{CoAP data: 3 \times 5 (CoAP structure) + 2 \times 2 Uri-Path-Abbrev + 2 \times 1 \texttt{C\_I / true} + 101 from \rfc{9528}} (-20\%).

      \bigskip

      Negligible over lifetime. Significant during mass onboarding (\ietfdraft{ietf-lake-reqs}, straddles AKE-for-6TiSCH fragmentation boundary).

      \bigskip

    \item[\color{gray}EST/cBRSKI] \color{gray}Eases management of .well-known coordination with HTTP.

      \bigskip

    \item[\color{gray}\texttt{-responses}] \color{gray}``If you queried me for /.well-known/core?a=b, you'd get \$\{payload\}''
  \end{description}

  \vspace{1.5cm}

  \color{gray}Ideally: Server MUST implement (in \ietfdraft{ietf-ace-edhoc-oscore-profile}, incoming in cBRSKI)
\end{frame}

\end{document}
