\input{shared/ietf-slides.tex}

\title{URI-Path abbreviation in CoAP}
\subtitle{\ietfdraft{ietf-core-uri-path-abbrev-05}}
\author{\textit{Christian~Amsüss}, Michael~Richardson}
\date{CoRE at IETF126 / Vienna, 2026-07-23}

\begin{document}

\frame{\titlepage}

\begin{frame}{\color{gray}Why?}\Large\color{gray}
  GET /.well-known/core has 17 bytes of Uri-Path.

  \bigskip

  EDHOC was unhappy.

  \bigskip

  cBRSKI is unhappy.

  \bigskip

  IETFers are jealous of other SDOs\footnote{LwM2M's \texttt{/rd} is a BCP190 no-go}
\end{frame}

\begin{frame}{\color{gray}Solution}\Large\color{gray}
  Numeric Uri-Path-Abbrev option.

  \bigskip

  \begin{tabular}{l|l}
    Abbreviated & Expanded \\ \hline
    Uri-Path: 0 \hspace{1cm} & Uri-Path: ``.well-known'', ``core'' \\
    \texttt{d0 00} & \texttt{bb . w e l l - k n o w n 04 c o r e} \\
    2 & 17 \\
  \end{tabular}

  \bigskip

  Critical. Safe-to-forward\footnote{even though Uri-Path is not}.

  \bigskip

  Uri-Host (3), Uri-Port (7), \textbf{Uri-Path-Abbrev (13)}, Uri-Query (15).
\end{frame}

\begin{frame}{Post-WGLC: -05 published}\Large
  \framesubtitle{Addressing WGLC comments}

  Worked in reviews (and PRs!) from Esko and Marco.
  
  \bigskip

  Jon and Mikolai reported from implementations.

  \bigskip

  \begin{itemize}
    \item ``reject'' was ambiguous, now ``refuse'' a request at access control.
      \bigskip
    \item Editorial changes, including in abstract.
  \end{itemize}
\end{frame}

\begin{frame}{IANA review}\Large
  \framesubtitle{Thanks to David, Amanda and Sabrina}
  \begin{itemize}
    \item IETF review vs. expert instructions

      \bigskip

      Plan: Move text into body, target requesters and reviewers, reference from IANA considerations.
      \bigskip
    \item Name of registry
  \end{itemize}

  \bigskip

  Can this happen in parallel with the…
\end{frame}

\begin{frame}{Next steps}\Large
  \begin{itemize}
    \item Shepherd review (Carsten)
  \end{itemize}
\end{frame}

\end{document}
