\input{shared/ietf-slides.tex}

\title{URI-Path abbreviation in CoAP}
\subtitle{\ietfdraft{ietf-core-uri-path-abbrev-02}}
\author{\textit{Christian~Amsüss}, Michael~Richardson}
\date{2025-11-07, CoRE at IETF124}

\begin{document}

\frame{\titlepage}

\begin{frame}{Why?}\Large
  GET /.well-known/core has 17 bytes of Uri-Path.

  \bigskip

  EDHOC was unhappy.

  \bigskip

  cBRSKI is unhappy.

  \bigskip

  IETFers are jealous of other SDOs\footnote{LwM2M's \texttt{/rd} is a BCP190 no-go}
\end{frame}

\begin{frame}{Solution}\Large
  Numeric Uri-Path-Abbrev option.

  \bigskip

  \begin{tabular}{l|l}
    Abbreviated & Expanded \\ \hline
    Uri-Path: 0 \hspace{1cm} & Uri-Path: ``.well-known'', ``core'' \\
    \texttt{d0 00} & \texttt{bb . w e l l - k n o w n 04 c o r e} \\
    2 & 17 \\
  \end{tabular}

  \bigskip

  Critical. Safe-to-forward\footnote{even though Uri-Path is not}.

  \bigskip

  Uri-Host (3), Uri-Port (7), \textbf{Uri-Path-Abbrev (13)}, Uri-Query (15).
\end{frame}

\begin{frame}{History}\Large
  \begin{description}
    \item[\textasciitilde 2012] considered but not prioritized  -- too early.
    \item[2021] more generic precursor suggested\footnote{interim meeting, 2021-05-12, ``Common option compression''}  -- too broad.
    \item[IETF123] EST consideres workaround; quick -00.

    \item[\ldots] Simplified into WG -02:
      \begin{itemize}
        \item Single uint value.
        \item Mutually exclusive with Uri-Path.
      \end{itemize}
  \end{description}
\end{frame}

\begin{frame}{Applications}\large
  \begin{description}[\texttt{-responses}]
    \item[EDHOC] first 3 message total: -30 byte down to 122\footnote{CoAP data: 3 \times 5 (CoAP structure) + 2 \times 2 Uri-Path-Abbrev + 2 \times 1 \texttt{C\_I / true} + 101 from \rfc{9528}} (-20\%).

      \bigskip

      Negligible over lifetime. Significant during mass onboarding (\ietfdraft{ietf-lake-reqs}, straddles AKE-for-6TiSCH fragmentation boundary).

      \bigskip

    \item[EST/cBRSKI] Eases management of .well-known coordination with HTTP.

    \item[\texttt{-responses}] ``If you queried me for /.well-known/core?a=b, you'd get \$\{payload\}''
  \end{description}

  \vspace{1.5cm}

  Ideally: Server MUST implement (in \ietfdraft{ietf-ace-edhoc-oscore-profile}, incoming in cBRSKI)
\end{frame}

\begin{frame}{Status}\Huge
  Implemented.

  \vspace{1.5cm}

  Ready.
\end{frame}

\begin{frame}{Open issues}\Large
    \begin{itemize}
        \item Explain use cases -- open for more examples \href{https://github.com/core-wg/uri-path-abbrev/issues/15}{\#15}
          \bigskip
        \item Proliferation of well-known vs. discovery? \href{https://github.com/core-wg/uri-path-abbrev/issues/29}{\#29}
          \bigskip
        \item Reap benefits from corr-clar if possible in time \href{https://github.com/core-wg/uri-path-abbrev/issues/28}{\#28}
          \begin{itemize}\large
            \item If one proxy does an odd thing, another must fix it. \href{https://github.com/core-wg/corrclar/issues/51}{cc\#51}
            \item Failover: handle 5.02 Bad GW due to 4.02 Bad Option NON-issues. \href{https://github.com/core-wg/corrclar/issues/52}{cc\#52}
          \end{itemize}
          \bigskip
        \item Does anyone need what was removed since -00? \href{https://github.com/core-wg/uri-path-abbrev/issues/23}{\#23}
    \end{itemize}
\end{frame}

\begin{frame}{Next steps}\Huge
  Dependents are approaching WGLC.

  \vspace{1.5cm}

  Can we keep the pace?
\end{frame}

\end{document}
