\input{shared/ietf-slides.tex}

% about the presentation
\title{Short Paths in CoAP}
\subtitle{\ietfdraft{amsuess-core-shopinc-01}}
\author{\textit{Christian~Amsüss}, Michael~Richardson}
\date{2025-08-27, CoRE interim}

\begin{document}

\frame{\titlepage}

\begin{frame}{Why?}\Large
  GET /.well-known/core has 17 bytes of Uri-Path.

  \bigskip

  EDHOC was unhappy.

  \bigskip

  cBRSKI is unhappy.

  \bigskip

  IETFers are jealous of other SDOs.
\end{frame}

\begin{frame}{Solution}\Large
  Numeric option.

  \bigskip

  Look up number, expand to Uri-Path.

  e.\,g. \texttt{d0 00} → \texttt{bb . w e l l - k n o w n 04 c o r e}

  \bigskip

  Critical. Safe-to-forward, even though Uri-Path is not.
\end{frame}

\begin{frame}{Interactions}\large
  \begin{block}{With Uri-Query}
    Simple if we pick a number < Uri-Query.

    That number is 13.
  \end{block}

  \begin{block}{With itself}
    Specified per number.

    Typical (e.\,g. cBRSKI): Treat like added Uri-Path strings.
  \end{block}

  \begin{block}{Proxy-Uri}
    Yikes. Ceterum censeo…

    Small interop hazard, maybe none.
  \end{block}

  \begin{block}{Uri-Path}
    Prefix? See issue \href{https://github.com/chrysn/shopinc/issues/9}{\#9}.
  \end{block}
\end{frame}

\begin{frame}{Open questions}\Large
    \begin{itemize}
        \item Number 13 justified?
        \item Are we encouraging excessive .well-known-ness?
        \item Prepopulate with EDHOC?
        \item Presenting multiple-option handling: List? Default-or-custom?
        \item IANA interactions \href{https://github.com/chrysn/shopinc/issues/2}{\#2}
    \end{itemize}
    … or can we already go on to
    \begin{itemize}
        \item Bikeshedding option and document name.
        \item Can we ship it in time for cBRSKI to not need probing?
    \end{itemize}
\end{frame}

\end{document}
